---
title: "Quakes app"
author: "Karen Reijneveld"
date: "21 oktober 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Fiji Earthquakes

From the available datasets in R, I chose 'quakes' for my Shiny app. 

The dataset gives the locations of 1000 seismic events of MB > 4.0. 
The data frame contains 1000 observations of 5 numeric variables:  

* lat: 	 Latitude of event  
* long:  Longitude of event
* depth: Depth (km)  
* mag: 	 Richter Magnitude  
* stations:  Number of stations reporting  

```{r data, message = FALSE}
library(dplyr)
data(quakes)
attach(quakes)
```

## The app

The app on next slide shows the earthquakes on a map.      


* You can choose to show the magnitude, depth or the number of stations on the map.   

* You can use sliders to filter the data for magnitude and depth.   

* The legend adapts to your choices.  

* Help information is provided (click on question marks)  

http://rpubs.com/KReij/542012 


## Quakes app
```{r}
knitr::include_app("https://reijn164.shinyapps.io/MyShinyApp/", height = "500px")
```
## Additional info
The distribution of the data is not very clear on a map like this. 
In a next version of the app, it would be nice to add a visualisation of the distribution(s).
```{r, fig.height=3}
par(mfrow=(c(1,2)))
hist(mag, col = "green", xlab = "Magnitude", main="")
hist(depth, col = "blue", xlab = "Depth (km)", main= "")
abline(v=mean(depth))
```
Some calculations:  
The mean depth of the earthquakes is `r round(mean(depth))` km.  
`r 100*count(filter(quakes, mag >5))/count(quakes)`% of the earthquakes has a magnitude higher than 5.